Performance Comparison of Common Face Detection APIs in Video Stills from Professional Tennis Matches

### 2018-01-29 paper/paper.Rmd
ASA style

---
title: "Detecting Facial Expressions in Video Stills from Professional Tennis Matches"
author: "Stephanie Kobakian, Mitchell O'Hara-Wild, Dianne Cook, Stephanie Kovalchik"
date: "20 September 2017"
output: bookdown::pdf_document2
toc: false
fig_caption: yes
number_sections: false
fontsize: 11pt
documentclass: article
geometry: margin=1in
header-includes:
    - \usepackage{setspace}\doublespacing
bibliography: references.bib
biblio-style: chicago
link-citations: true
---

>>>>

---
title: "Performance Comparison of Common Face Detection APIs in Video Stills from Professional Tennis Matches"
authors: 
- name: Stephanie Kobakian
  affiliation: Monash University 
- name: Mitchell O'Hara-Wild
  affiliation: Monash University
- name: Dianne Cook
  affiliation: Monash University
- name: Stephanie Kovalchik
  affiliation: Victoria University and Tennis Australia
output: rticles::asa_article
toc: false
fig_caption: yes
number_sections: false
fontsize: 11pt
documentclass: article
geometry: margin=1in
header-includes:
    - \usepackage{setspace}\doublespacing
bibliography: references.bib
biblio-style: chicago
link-citations: true
---
